Title

### 2024-05-13 paper/main.tex
Updates

\begin{enumerate}
	\item Biased towards sparse graphs.
	\item Algorithms making obvious mistakes: These algorithms often 
		make very obvious mistakes, making it harder for the user
		to trust them.
	\item Difficulties in choosing an algorithm: For any given dataset, the
		user need to make a choice of the algorithm. Given that these
		algorithms work very differently, it can be difficult to make a
		choice. Additionally, each of these algorithms have
		hyperparameters and choices to make for them, making it
		difficult. As there is no way to evaluate the performance of 
		these algorithms on our dataset.
\end{enumerate}
Both in the cases when the DAG is an output of an algorithm or when constructed
by hand, it is vital to test these models against data before using them for
making any inference.

>>>>

\begin{enumerate}
	\item Biased towards sparse graphs.
	\item Algorithms making obvious mistakes: These algorithms often make
		very obvious mistakes, making it harder for the user to trust
		them.
	\item Difficulties in choosing an algorithm: For any given dataset, the
		user need to make a choice of the algorithm. Given that these
		algorithms work very differently, it can be difficult to make a
		choice. Additionally, each of these algorithms have
		hyperparameters and choices to make for them, making it
		difficult. As there is no way to evaluate the performance of
		these algorithms on our dataset.
\end{enumerate}

Both in the cases when the DAG is an output of an algorithm or when constructed
by hand, it is vital to test these models against data before using them for
making any inference.
